\documentclass[11pt,a4paper]{moderncv}

%----------------------------------------------------------------------------------------
%   CONFIGURATIONS
%----------------------------------------------------------------------------------------
\moderncvstyle{classic} % Style options: 'casual' (default), 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}    % Color options: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[scale=0.82]{geometry}
\setlength{\hintscolumnwidth}{70pt}  

\usepackage{lmodern}    % Latin Modern font for special characters if needed
\usepackage{amsmath,amssymb}



%----------------------------------------------------------------------------------------
%   PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
\name{Mehdi}{Dehghani Firouzabadi}
\title{AI Researcher \& Developer}                              
\address{Tehran, Iran}{}{}                            
\phone[mobile]{+98-9124764062}                         
\extrainfo{\href{https://x.com/m_dehghani_}{X: m\_dehghani\_}}
\email{mehdi274787@gmail.com}                          




%----------------------------------------------------------------------------------------
\begin{document}
	\makecvtitle
	
	%----------------------------------------------------------------------------------------
	%   EDUCATION
	%----------------------------------------------------------------------------------------
	\section{Education}
	\cventry{2020 -- Present}{M.Sc. in Computer Science (Data Mining)}{Tarbiat Modares University}{Tehran, Iran}{}{
		\textit{Thesis Title:} ``An Improved Generative Model Based on Diffusion'' \\
	}
		
	\cventry{2002 -- 2005}{B.Sc. in Computer Engineering (Software)}{Yazd University}{Yazd, Iran}{}{
		Graduated in seven semesters with second rank. \\
		\textit{Thesis Title:} ``Design and Implementation of a Real Estate Web System''
	}
	
	%----------------------------------------------------------------------------------------
	%   PROFESSIONAL EXPERIENCE
	%----------------------------------------------------------------------------------------
	\section{Professional Experience}
	
	\cventry{2024 -- Present}{Startup MMMF}{}{Tehran, Iran}{}{
	\begin{itemize}
		\item Developed a time series forecasting framework for \textbf{multivariate} data using deep learning models.
	\end{itemize}
	}
	\cventry{2020 -- Present}{Freelance Instructor}{}{Tehran, Iran}{}{
	\begin{itemize}
		\item Providing instruction in \textbf{Python Programming}, \textbf{Machine Learning}, and \textbf{Deep Learning}.
	\end{itemize}
	}	
	\cventry{2015 -- 2019}{Rahian Software Development}{}{Tehran, Iran}{}{
	\begin{itemize}
       	\item Collaborated in developing an intelligent gate barrier system designed for parking lot access control.
	\end{itemize}
	}
	\cventry{2014 -- 2015}{Sepanta Robotic Research Foundation (SRRF)}{}{Tehran, Iran}{}{
	\begin{itemize}
        \item Collaborated in the design and implementation of an \textbf{OCR system} for Persian scripts.
	\end{itemize}
	}
	\cventry{2009 -- 2014}{Mehregan Danesh Pazhooh}{}{Tehran, Iran}{}{
	\begin{itemize}
		\item Collaborated on the development of an \textbf{in-house CRM software}.
	\end{itemize}
	}
	
		%----------------------------------------------------------------------------------------
	%   RESEARCH INTERESTS
	%----------------------------------------------------------------------------------------
	\section{Research Interests}
	\begin{itemize}
		\cvitem{}{
			\item Machine Learning and Deep Learning methodologies
			\item Deep Generative Models, including Diffusion Models and Rectified Flow Models 
			\item Inverse Problems using Score-based Diffusion Models
			\item Exploration of Latent Space through Dimensionality Reduction Methods
			\item Time Series Forecasting
			\item Investigating the influence of consciousness on the generation of random numbers
		}
	\end{itemize}
	

	%----------------------------------------------------------------------------------------
	%   TECHNICAL SKILLS
	%----------------------------------------------------------------------------------------
	\newpage
	\section{Technical Skills}
	\cvitem{Programming Languages}{Delphi, C++, Python}
	\cvitem{Python IDEs}{Jupyter Notebook, Google Colab, VSCode, PyCharm, Cursor}
	\cvitem{Python Libraries}{
		PyTorch, Pandas, NumPy, Matplotlib, Scikit-Learn, SciPy, OpenCV, Seaborn, Darts (time series forecasting)
	}
	\cvitem{Model Development Tools}{
		Hydra (configuration management), TensorBoard (visualization), MLflow, Optuna (hyperparameter optimization), Ray (deep learning fine-tuning), Captum (Integrated Gradients for feature selection)
	}
	\cvitem{Tools \& Infrastructure}{Git, Linux, LaTeX, Word, Excel, PowerPoint}

	
	

	
	%----------------------------------------------------------------------------------------
	%   PUBLICATIONS
	%----------------------------------------------------------------------------------------
	\section{Publications}
	\cvitem{[1]}{H. Sagha, S. B. Shouraki, H. Khasteh and M. Dehghani, \emph{``Real-Time IDS Using Reinforcement Learning,''} in \textbf{IEEE Second International Symposium on Intelligent Information Technology Application}, Shanghai, 2008.}
	
	\cvitem{[2]}{H. Sagha, S. Kasaei, E. Enayati, M. Dehghani, \emph{``Finding Sparse Features in Face Detection Using Genetic Algorithms,''} in \textbf{IEEE International Conference on Computational Cybernetics}, 2008.}
	
	%----------------------------------------------------------------------------------------
	\section{Academic Activities}
	\cvitem{}{
		Presented various academic topics during university courses, including:  
		Pitch Estimation in Speech using Fuzzy Methods, Rotation-Invariant Face Recognition, Voice Transformation and Modification, Time-Varying Spectrum Estimation by Fuzzy Methods, Virtual Reality (VR), Multi-objective Optimization using Evolutionary Algorithms, Tensor Methods in Computer Vision and Deep Learning, Discrete Contrastive Diffusion, Contrastive Clustering, Denoising Diffusion Models.
	}

	
	
	%----------------------------------------------------------------------------------------
	%   HONORS & AWARDS
	%----------------------------------------------------------------------------------------
	\section{Honors \& Activities}
	\begin{itemize}
	\cvitem{}{
		\item Ranked 25th nationally in the M.Sc. Computer Engineering Entrance Exam (2006).
		\item Ranked 37th nationally in the M.Sc. Computer Science Entrance Exam (2006).
		\item Provincial winner in the 4th Kharazmi Young Festival for ``Real-time Voice Conversion Software'' (2002).
		\item Provincial winner in the 5th Kharazmi Young Festival for ``Machine Vision'' (2003).
		\item Official software registration at the High Council of Informatics, Management and Planning Organization (2006).
		\item Winner of Sharif Business Plan Competition (2007) for ``Mobile Text-to-Speech Software''.
		\item Selected for the 2nd Innovation Festival, University of Tehran (2017) for ``Cloud-based System for Attendance Tracking''.
		\item Selected for the 3rd Innovation Festival, University of Tehran (2018) for ``Smart System for Book Provision and Exchange''.
		\item Selected for IdeaTap Event, Qom Science and Technology Park (2019) for ``Specialized Simulator for Sensitive and Critical Environments''.
		\item Selected for the Innovation Festival, University of Tehran (2020) for ``VR and AR-based Simulator for Sensitive and Critical Environments''.
		}
	\end{itemize}
	
\end{document}
